---
title: "Biodiversity Index Map of the University Forest Caldern"
output: 
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rgdal)
library(link2GI)
library(mapview)
library(raster)
species = readOGR("../page/mof_realdata.shp")
nam = readRDS("../page/labels_crowns.rds")
names(species) = nam
```
[Return](https://goergen95.github.io/mof_caldern.github.io/)


## Tree Biodiversity Index of the University Forest Caldern
This is the map of the tree species biodiversity for the University Forest Caldern.
The index is based on a 30 meter environment for every tree and then [calculating](https://github.com/GeoMOER-Students-Space/mpg-envinfosys-teams-2018-rs_18_axmideda/blob/master/src/011_structure_values.R#L173) the Shannon-Weaver Entropy index for the different species present in the neighbourhood. At this scale, it gives a good overview of biodiversity hotspots in the forest area.
By clicking on ploygons you will get addtional information including:
```{r echo = FALSE}
df = data.frame(variable = names(species))
expl = c("Tree Identification Number",
         "Maximum Height",
         "Crown Area (in meter)",
         "Average vertical Density",
         "Number of pixels classified as Beech",
         "Number of pixels classified as Douglas Spruce",
         "Number of pixels classified as Oak",
         "Number of pixels classified as Spruce",
         "Total number of Pixels",
         "Percentage of maximum class",
         "Classification Result",
         "Number of trees in 1 acre environment",
         "Crown cover in 1 acre environment",
         "Average free space per stem in 1 acre environment",
         "Number of direct neighbors",
         "Entropy value based on number of tress ",
         "Entropy value based on species in 10 meter environment",
         "Entropy value based on species in 30 meter environment",
         "Entropy value based on species in one acre environment"
         )
df$explanation = expl
df

```


```{r echo = FALSE, warning=FALSE}
greenred = colorRampPalette(c("green","yellow","red"))

 mapview::mapview(species, zcol = c("div30"),
                       color = "black",
                       at = seq(0,1.4,0.1),
                       col.regions = greenred(15),
                       na.color = "grey",
                       lwd = 0.1,
                       legend = TRUE,
                  layer.name = "Biodiversity Index (30 meters)")
```


[Return](https://goergen95.github.io/mof_caldern.github.io/)
