---
title: "Vertical Vegetation Density Map of the University Forest Caldern"
output: 
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rgdal)
library(link2GI)
library(mapview)
library(raster)
species = readOGR("../page/mof_realdata.shp")
nam = readRDS("../page/labels_crowns.rds")
names(species) = nam
```
[Return](https://goergen95.github.io/mof_caldern.github.io/)


## Vertical Vegetation Density Map of the University Forest Caldern
This is the map of vertical density of the University Forest Caldern. This [index](https://github.com/GeoMOER-Students-Space/mpg-envinfosys-teams-2018-rs_18_axmideda/blob/master/src/011_structure_values.R#L97) was calculated by averaging the proportion of above ground LIDAR returns from all returns for each individual tree. The code to calculate this index can be accessed here. By clicking on ploygons you will get addtional information including: 

```{r echo = FALSE}
df = data.frame(variable = names(species))
expl = c("Tree Identification Number",
         "Maximum Height",
         "Crown Area (in meter)",
         "Average vertical Density",
         "Number of pixels classified as Beech",
         "Number of pixels classified as Douglas Spruce",
         "Number of pixels classified as Oak",
         "Number of pixels classified as Spruce",
         "Total number of Pixels",
         "Percentage of maximum class",
         "Classification Result",
         "Number of trees in 1 acre environment",
         "Percantage of crown cover in 1 acre environment",
         "Average free space per stem in 1 acre environment",
         "Number of direct neighbors",
         "Entropy value based on number of tress ",
         "Entropy value based on species in 10 meter environment",
         "Entropy value based on species in 30 meter environment",
         "Entropy value based on species in one acre environment"
         )
df$explanation = expl
df

```


```{r echo = FALSE, warning=FALSE}
intens = colorRampPalette(c("lemonchiffon","darkolivegreen3","forestgreen"))
mapview::mapview(species, zcol = c("dens"),
                 color = "grey",
                 at = seq(0,1,0.02),
                 col.regions = intens(51),
                 na.color = "grey",
                 lwd = 0.1,
                 legend = TRUE,
                 layer.name = "Vertical Vegetation Density")

```

[Return](https://goergen95.github.io/mof_caldern.github.io/)

