---
title: "Direct Neighbours Map of the University Forest Caldern"
output: 
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rgdal)
library(link2GI)
library(mapview)
library(raster)
species = readOGR("../page/mof_realdata.shp")
nam = readRDS("../page/labels_crowns.rds")
names(species) = nam
```
[Return](https://goergen95.github.io/mof_caldern.github.io/)


## Direct Neighbour Map of the University Forest Caldern

This is the map of the number of direct neighbours for the University Forest caldern. This index was calculated by a ten centimeter buffer and counting the intersecting polygons in the neihborhood of each segment. The code to calculate the [direct neigbours](https://github.com/GeoMOER-Students-Space/mpg-envinfosys-teams-2018-rs_18_axmideda/blob/master/src/011_structure_values.R#L140) can be seen here. It thus indicates some measure of competition. By clicking on ploygons you will get addtional information including:
```{r echo = FALSE}
df = data.frame(variable = names(species))
expl = c("Tree Identification Number",
         "Maximum Height",
         "Crown Area (in meter)",
         "Average vertical Density",
         "Number of pixels classified as Beech",
         "Number of pixels classified as Douglas Spruce",
         "Number of pixels classified as Oak",
         "Number of pixels classified as Spruce",
         "Total number of Pixels",
         "Percentage of maximum class",
         "Classification Result",
         "Number of trees in 1 acre environment",
         "Percantage of crown cover in 1 acre environment",
         "Average free space per stem in 1 acre environment",
         "Number of direct neighbors",
         "Entropy value based on number of tress ",
         "Entropy value based on species in 10 meter environment",
         "Entropy value based on species in 30 meter environment",
         "Entropy value based on species in one acre environment"
         )
df$explanation = expl
df

```


```{r echo = FALSE, warning=FALSE}
intens = colorRampPalette(c("khaki1","hotpink4","gray0"))
mapview::mapview(species, zcol = c("NDirNeigh"),
                 color = "grey",
                 at = seq(1,14,1),
                 col.regions = intens(14),
                 na.color = "forestgreen",
                 lwd = 0.1,
                 legend = TRUE,
                 layer.name = "Direct Neighbours")

```

[Return](https://goergen95.github.io/mof_caldern.github.io/)

