---
layout: page
title: "Biodiversity Index Map"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rgdal)
library(link2GI)
library(mapview)
library(raster)
species = readOGR("../assets/maps/mof_realdata.shp")
nam = readRDS("../assets/maps/labels_crowns.rds")
names(species) = nam
```
## Overview of the Biodiversity Index at a 10 meters environment

This is a preview of the map for tree species biodiversity in a 30 meter environment for the University Forest Caldern.
Unfortunatley, due to file size limitations on github, the fully interactive version of the [map](http://seminar.environmentalinformatics-marburg.de/Seminar_RS/biodiversity30.html) is hosted by servers of the Environmental Informatics Department of the University of Marburg. Be aware that the file size is above 100 MB.


The index is based on a 10 meter environment for every tree and then [calculating](https://github.com/GeoMOER-Students-Space/mpg-envinfosys-teams-2018-rs_18_axmideda/blob/master/src/011_structure_values.R#L173) the Shannon-Weaver Entropy index for the different species present in the neighbourhood. At this scale, it gives a good overview of biodiversity hotspots in the forest area.

```{r echo = FALSE, warning=FALSE}
greenred = colorRampPalette(c("green","yellow","red"))

mapview::mapview(species, zcol = c("div10"),
                 color = "black",
                 at = seq(0,1.4,0.1),
                 col.regions = greenred(15),
                 na.color = "grey",
                 lwd = 0.1,
                 legend = TRUE,
                 layer.name = "Biodiversity Index (10 meters)")
```


[
